Observed vs. Simulated Year Comparison

### 2023-12-05 03-post-process/output-plots-children/09-composite-rates.Rmd
Fix tiny bugs in Rmd output
Fix years in phi_Rb_Sa composite rates
Old version broken for simulation case

```{r spawners-per-return-fn}
# function to calculate the survival term for a given origin, population, and combo of ages
f = function(o, j, include_age3) {
  # spawning adult abundance
  Sa = post_subset(post, sub_index("^Sa[year,age,origin,pop]", year = ".+", age = ".+", origin = o, pop = j), matrix = TRUE)

  # adults at estuary
  Rb = post_subset(post, sub_index("^Rb[year,age,origin,pop]", year = 2:33, age = ".+", origin = o, pop = j), matrix = TRUE)

@@

```{r spawners-per-return-all-ages, fig.width = p4_width, fig.height = p4_height}

# loop over populations
# includes all ages
mypar()
junk = sapply(1:jags_data$nj, plot_f, include_age3 = TRUE)
axis_labels("Return Year", "Spawners per Returning Adult (All Ages)")
```

### Ages 4&5 {-}

```{r spawners-per-return-old-ages, fig.width = p4_width, fig.height = p4_height}

# loop over populations
# includes only ages 4 and 5
mypar()
junk = sapply(1:jags_data$nj, plot_f, include_age3 = FALSE)
axis_labels("Brood Year", "Spawners per Returning Adult (Ages 4&5)")
```

>>>>

```{r spawners-per-return-fn}
# function to calculate the survival term for a given origin, population, and combo of ages
f = function(o, j, include_age3) {
  # spawning adult abundance
  Sa = post_subset(post, sub_index("^Sa[year,age,origin,pop]", year = ts_yrs, age = ".+", origin = o, pop = j), matrix = TRUE)

  # adults at estuary
  Rb = post_subset(post, sub_index("^Rb[year,age,origin,pop]", year = ts_yrs, age = ".+", origin = o, pop = j), matrix = TRUE)

@@

```{r spawners-per-return-all-ages, fig.width = p4_width, fig.height = p4_height}
# loop over populations
# includes all ages
mypar()
junk = sapply(1:jags_data$nj, plot_f, include_age3 = TRUE)
axis_labels("Return Year", "Spawners per Returning Adult (All Ages)")
```

#### Ages 4&5 {-}

```{r spawners-per-return-old-ages, fig.width = p4_width, fig.height = p4_height}
# loop over populations
# includes only ages 4 and 5
mypar()
junk = sapply(1:jags_data$nj, plot_f, include_age3 = FALSE)
axis_labels("Brood Year", "Spawners per Returning Adult (Ages 4&5)")
```
